### 2015-05-10 thesis/thesis/chap3/chap3.tex
added coop

In this section, we discuss the experiments we performed for our
scenarios to validate the applicability and performance of our
proposed methods in realistic environments. We created a pool of
web services and populated most of their \emph{QoS} parameters
from a real world web service dataset
\cite{DBLP:conf/smc/Al-MasriM09a}. We implemented the simulations
using Java and executed the simulations on an Intel Xeon X3450
machine with 6GBs of memory. For other parameters missing from the
dataset, we used normal random distribution with parameters
estimated using the method of maximum likelihood.

@@

\begin{figure}[!t]
\centering
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[width=2.5in]{Figures/avg_task_ws_done.eps}
\includegraphics[width=2.5in]{Figures/avg_qos_ws_done.eps}
\includegraphics[width=2.5in]{Figures/avg_avail_ws_done.eps}
\caption{A comparison between our community model and the high availability community model, on communities of size 4,5,6 only. Part (a): Cumulative number of tasks succesfully done. Part
(b): Average QoS of tasks performed. (c) Average Community Service Availability} \label{fig_avail_method}
\end{figure}

Finally, in our last experiment, we compare our work with the work
in \cite{10.1109/TSC.2012.12} which we call it \emph{High
Availability Coalition} method, because of nature of their
community valuation function, which focuses on community
availability as main consideration. Their community formation
model is very different than ours, however we have been very
careful to make the experiment environment as fair and similar as
possible. We limited our maximum community size by 5 in order to
have communities with almost the same size. In their method, they
have used web services as backups rather than active collaborative
players, and they only get task when the first web service in an
ordered chain fails to perform the task. However with recent
advancement in cloud and hardware infrastructures availability is
less of an issue for web services, and web services are highly
available. Part(a) of figure \ref{fig_avail_method} shows our
method performs almost performs tasks successfully with rate of
three times more than \emph{High Availability Coalition} method
because of real cooperative nature and task distribution of our
algorithm. This result shows using web services as backups, and
not as real collabrative players is a huge waste of web service
capability since they have very low chance of getting jobs and its
the primary web service (the first in their coordination chain)
which does most of the work. The average quality of service of
tasks performed is also better since our method considers all
quality of service metrics mentioned in Table \ref{qosws}. Part(c)
shows the availability of community from end user point of view.
The \emph {High Availability Coalition} method almost has 100\%
uptime since they use web services as backups, so the chance of
job failing reduces significantly as community members increase.
In our method we have more chance of fail for each web service,
however with some subsiding, and hiring a few more web service
they can compensate the low chance of failure of web services in
our community.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary}\label{sec:conclusion-cha3}

>>>>

In this section, we discuss the experiments we performed for our
scenarios to validate the applicability and performance of our
proposed methods in realistic environments.
An XML SOAP based messaging system was implemented. We created a pool of web services and populated most of
their \emph{QoS} parameters from a real world web service dataset
\cite{DBLP:conf/smc/Al-MasriM09a}\footnote[1]{The implemented
environment includes the QWS dataset by Eyhab Al-Masri and Qusay
H. Mahmoud freely available at:
http://www.uoguelph.ca/\textasciitilde{}qmahmoud/qws/.}. To test
our methods, we formed around 10,000 random coalitions consisting
of 3 to 160 web services. In average, the communities were populated by 60 web
services. We implemented the
scenarios using Java and executed the experiments on an Intel Xeon
X3450 machine with 6GBs of memory.

@@

\begin{figure*}%[!t]
\centering
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[width=3in]{Figures/taxtation.eps}
\caption{Analysis of community subsiding coefficient $\lambda$ on
average community size (a), cost (b), number of tasks performed
(c), and average quality of service of tasks performed (d).}
\label{f_taxtation}
\end{figure*}

As mentioned in Section \ref{s:tax}, a solution to help the
community stabilize is to subside the community by a relative
coefficient ($\lambda$) so the value of $\lambda v(C)$ is divided
among the community members. We have analyzed the effect of
subsiding and the cost it incurs to our web service communities.
Figure \ref{f_taxtation} shows the results. In this experiment, we
have set a community with input task rate $R_C$ of 100 and having
web services throughput rate $Th_{ws}$ values from a normal
distribution with average 10 tasks per iteration and standard
deviation 2. Part (a) shows the community size increases in a
linear fashion as ($\lambda$) increases. However, the cost (Part
(b)) is having a slight exponential growth rate since, not only
($\lambda$) increases, but also the size of the community is
increasing slowly. Therefore, subsiding can be costly for larger
number of $\lambda$ values. Part (c) depicts the number of tasks
done by the community per iteration. It is obvious that with
$\lambda$ value of 1.3, which is 30\% of the community valuation,
the number of tasks done almost reaches the input task rate cap of
100 tasks per iteration. The average quality of tasks also has a
slight increase since the community will be able to afford better
and more web services to join the community (Part (d)). These
results show the effectiveness of our subsiding method and its
impact on the QoS. In fact, using more than 30\% of the community
valuation as subsidy is not very effective and is costly to
perform.

\begin{figure*}%[!t]In the previous experiment, we considered the scenario where all
web services are stable, will not leave the group, and will
fulfill their promised QoS for a good period of time. However, in
real world scenarios of web services, this is not always the case.
This is the reason why the community coordinator would be interested in paying
web services in order to keep the group reliable from the end
user's point of view.
\centerline{\includegraphics[width=6.8in]{Figures/tax_dyn.eps}}
\caption{Analysis of community subsiding coefficient $\lambda$
having web service different stability levels of $\tau$ on average
community size, number of tasks performed, average quality of
service, and average cost/income of communities.}
\label{fig_dynamic_taxtation}
\end{figure*}

In our next scenario, we have introduced the
new instability variable $\tau$ ranging from 0 to 1, 0 meaning web
services having no instability issues and will perform as they
claimed until the end of the experiment, and 1 meaning very
unstable web services, which will stop functioning on the first
iteration of the community distributing tasks. Figure
\ref{fig_dynamic_taxtation} illustrates the results of our
experiment having web services with average instability values of
0 to 0.5 and having relative subside value $\lambda$ of 1, 1.3,
1.6, and 2. The \emph{Cost/Income} charts on the right column show
that having subside value of 1.3 incurs the least cost and
increases the community income significantly. Subsiding values of
1.6 and 2 yield high cost to the community and only slightly
increase the community revenue. Moreover, the role of subsiding is
much more obvious when we have unstable web services. In scenarios
where web services are 100\% stable, the subsiding cost will
hardly be compensated by the community revenue.

\begin{figure*}%[!t]
\centering
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[width=2.5in]{Figures/s2_task_done.eps}
\includegraphics[width=2.5in]{Figures/s2_task_qos.eps}
\caption{Part (a): Cumulative number of tasks successfully done.
Part (b): Average QoS of tasks performed.} \label{performancemany}
\end{figure*}

In Figure \ref{performancemany}, we consider \emph{Web Services
and many Communities} scenario and we compare our dynamic
coalition formation solution with a method which ignores QoS
parameters and forms communities by allowing web services to join
only if they have enough requests for themselves. In other words,
web services can join a community when the request rate is less
than the throughput of all the member web services. We name this
method \emph{Random Formation} and use it as a benchmark for our
QoS-aware community formation process. In this scenario, each user
individually generates randomly between 0 to 10 number of tasks
per iteration, then the users target a community and direct their
requests to the chosen community. As the results illustrate, our
method forms better communities of web services improving
performance and satisfaction for both web services and
communities.

\begin{figure*}%[!t]
\centering
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[width=1.9in]{Figures/avg_task_ws_done.eps}
\includegraphics[width=1.9in]{Figures/avg_qos_ws_done.eps}
\includegraphics[width=1.9in]{Figures/avg_avail_ws_done.eps}
\caption{A comparison between our community model and the High
Availability Coalition model from \cite{10.1109/TSC.2012.12}. Part
(a): Cumulative number of tasks successfully done. Part (b):
Average QoS of tasks performed. Part (c): Average community
service availability} \label{fig_avail_method}
\end{figure*}

Finally, in our last experiment, we compare our model with the
solution proposed in \cite{10.1109/TSC.2012.12}, which we call
\emph{High Availability Coalition} model. In this method, the
community valuation function focuses on the community availability
as main consideration. The community formation model used in this
method is very different from ours, but we have been very careful
to make the experiment environment as fair and similar to ours as
possible. We limited our maximum community size to 5 in order to
have communities with almost the same size as in
\cite{10.1109/TSC.2012.12}. In the High Availability Coalition
model, the authors have used web services as backups rather than
active collaborative players, and those web services only get a
task when the first web service in an ordered chain fails to
perform that task. %However, with recent advancement in cloud and
%hardware infrastructures, availability is less of an issue for web
%services, and web services are highly available.
Part(a) of Figure \ref{fig_avail_method} shows that with our
method, the number of tasks successfully done is higher with a
rate of three times more than the High Availability Coalition
model thanks to the cooperative behavior of web services and the
task distribution process of our algorithm. This result shows that
using web services as backups, and not as real collaborative
players results in a considerable waste of web services capability
since services have very low chance of getting jobs and its the
primary web service (the first in the coordination chain) which
does most of the work. As shown in Part (b), the average quality
of service of tasks performed using our solution is also higher
since our method considers all quality of service metrics used. Part(c) shows the availability of
communities from the end user's point of view. The High
Availability Coalition model has almost 100\% uptime since web
services are used as backups, so the chance of job failing is
getting reduced significantly as community members increase. In
our method, we have more chance of failure for each web service.
However, with some subsidies and by hiring a few more web
services, the chance of failure of web services in our communities
can be lowered.

\subsection{Coopetitive Behavior}\label{sb:resutlscoop}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary}\label{sec:conclusion-cha3}
